NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models

### 2018-06-26 paper/paper_entailVis.tex
space saving
update task
adjust figures
grammar fix

%make paper compact
\setlength{\parskip}{0.04cm}
\setlength{\parindent}{0.7em}

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network models have obtained state-of-the-art performances for many linguistic tasks in natural language processing. However, this rapid progress also brings enormous challenges. The opaque nature of neural network model leads to hard-to-debug-systems and difficult to interpret mechanisms. Here, we introduce a visualization system that through a tight yet flexible integration between visualization elements and the underlying model allows a user to interrogate the model by perturbing the input, the internal state, and prediction while observing changes in other parts of the pipeline. We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states, and interpret and form hypothesize about fundamental model mechanisms such as attention.
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
\vspace{-4mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 \vspace{-4mm}
  \caption{
The interface of the NLIZE system. During exploration, we can filter through a large number of sentence pairs summarized in (a) and the current selected pair is displayed in (b). The model internal information (attention) is displayed in (d) and (e). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f). Finally, the high-level model structure and the updates to the model are summarized in (c).
}
% \vspace{-2mm}
\label{fig:teaser}
}

@@

%% if specified like this the section will be committed in review mode
% \acknowledgments{
% The authors wish to thank A, B, and C. This work was supported in part by
% a grant from XYZ (\# 12345-67890).}

>>>>

@@

%% Abstract section.
% What are we doing in this paper
\abstract{
With the recent advances in deep learning, neural network models have obtained state-of-the-art performances for many linguistic tasks in natural language processing. However, this rapid progress also brings enormous challenges. The opaque nature of a neural network model leads to hard-to-debug-systems and difficult-to-interpret mechanisms. Here, we introduce a visualization system that, through a tight yet flexible integration between visualization elements and the underlying model, allows a user to interrogate the model by perturbing the input, internal state, and prediction while observing changes in other parts of the pipeline. We use the natural language inference problem as an example to illustrate how a perturbation-driven paradigm can help domain experts assess the potential limitation of a model, probe its inner states, and interpret and form hypotheses about fundamental model mechanisms such as attention.
} % end of abstract

@@

%% Uncomment below to include a teaser figure.
% \teaser{
%   \centering
%   \includegraphics[width=\linewidth]{CypressView}
%   \caption{In the Clouds: Vancouver from Cypress Mountain. Note that the teaser may not be wider than the abstract block.}
% 	\label{fig:teaser}
% }
\teaser{
\vspace{-4mm}
 % \includegraphics[width=0.78\linewidth]{teaser}
 \includegraphics[width=1.0\linewidth]{teaser.pdf}
 \centering
 \vspace{-6mm}
  \caption{
The interface of the proposed system. During exploration, we can filter through a large number of sentence pairs summarized in (a). the current selected pair is displayed in (b). The model internal information (attention) is displayed in (d) and (e). The predicted probability (one of three labels: \emph{neural}, \emph{entailment}, \emph{contradiction}) is shown in the barycentric coordinate in (f). Finally, the high-level model structure and the updates to the model are summarized in (c).
}
% \vspace{-2mm}
\label{fig:teaser}
}

@@

%% if specified like this the section will be committed in review mode
\acknowledgments{
The authors wish to thank A, B, and C. This work was supported in part by
a grant from XYZ (\# 12345-67890).
}
